---
title: "Untitled"
author: "Wiktoria Urantowka"
date: "7/24/2017"
output: html_document
---
#Reporoducuble Research#
##Project 1##

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Code for reading in the dataset & loading packages
```{r}
rm(list=ls())
setwd("/Users/quora1/Desktop/DataScience/5_Reproducible_Research/workDir")
library("zoo")
library("ggplot2")
data<-read.csv("./activity.csv",stringsAsFactors=FALSE) 
head(data)
```

2. Histogram of the total number of steps taken each day

```{r, echo=TRUE}
sumday<- aggregate(data$steps, list(date = data$date), sum)
hist(sumday[,2], main = "sum of steps per day")
```

3. Mean and median number of steps taken each day
```{r, echo=TRUE}
mean <-mean(sumday[,2],na.rm=TRUE)
median <-median(sumday[,2],na.rm=TRUE)
mean
median
```

4. Time series plot of the average number of steps taken
```{r, echo=TRUE}
with(data,plot(interval, steps, type="l", main='steps per 5 minut interval'))
```

5. The 5-minute interval that, on average, contains the maximum number of steps
```{r, echo=TRUE}
sum_interval<- aggregate(data$steps, list(interval = data$interval), sum,na.rm=TRUE)
max_step_interval<-sum_interval$interval[which.max(sum_interval$x)]
max_step_interval
```

6. Code to describe and show a strategy for imputing missing data
 
 Replacing NA by interval mean
```{r, echo=TRUE}
new<-na.aggregate(data$steps, by = data$interval)
data[,1] <- new
head(data)
```

7. Histogram of the total number of steps taken each day after missing values are imputed
```{r, echo=TRUE}
new.sumday<- aggregate(data$steps, list(date = data$date), sum)
hist(new.sumday[,2])
```
 Please note, after replacing NA by mean values, mean and median are equal.
```{r, echo=TRUE}
mean <-mean(new.sumday[,2])
median <-median(new.sumday[,2])
mean
median
```

8 Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends (and the steps required for it's computation)
```{r, echo=TRUE}
weekday<-as.POSIXlt(data$date)$wday
data[,4]<-as.numeric(weekday)
data$weektime<- ifelse(data$V4 >= 6, "weekend", "weekday")
data$weektime<-as.factor(data$weektime)
qplot(interval,steps,data=data,geom="line",facets=weektime~., ylab= "Number of steps",type = "ðš•")
```

Note, There is more variation in the average number of steps taken during the weekend than during the week days.


